\documentclass{article}
\begin{document}

\title{CONCEPT PAPER ON RESEARCH ON HOSTELS AROUND MAKERERE}
\author{Nangwale Joshua}
\maketitle

\section{Introduction}
Makerere University is one the largest public universities in Uganda and currently has almost 50,000 students. During the course of their study, the majority of students stay on campus in one the halls or in the immediate vicinity to offer convenience. There are currently 9 halls of residence on campus i.e. Lumumba, Livingstone, Nkrumah, Mitchel, University hall, Mary Stuart, Complex and Africa. These however lack the capacity to accommodate all students and thus many find themselves opting for private hostels located within close proximity to the university.

\section{Problem statement}
Selecting a suitable hostel for new entrants/freshmen to the university poses a challenge as there are several criteria being looked at. There is however limited information available to such individuals to aid them in their hunt for suitable accommodation. This makes the search process long and tedious with no guarantee of finding their ideal living arrangements.

\section{Proposed solution}
Carrying out research on the available hostels within the Makerere University to avail more information on the subject.

\section{Objective}
To gather and analyse information on the various hostels around  Makerere University .

\subsection{Specific objectives}
\begin{itemize}
\item Obtain pricing information on rooms .
\item Obtain location information of hostels.
\item Obtain information on hostel facilities.
\end{itemize}

\section{Methodology}
The research shall be carried out by visiting the various locations in question and conducting interviews with relevant personnel i.e. custodians, current residents/students. The pricing of the rooms will be the principal focus of the research as it is deemed one of the most important aspects factored in when deciding on a hostel.Whether the hostel rooms are self contained willl also be ascertained,as well the availability of hostel shuttles to transport students to and from campus. The location (GPS) of the hostel shall also be recorded to ease in locating the hostels to those unfamiliar with the area. Images shall aslo be taken of the hostel to give a representation of the general decor and facilities.







\end{document}

